---
title: "lab_report_knapsack"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lab_report_knapsack}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Ass4a3ht2020)
```

# Answers from Problem 4

```{r}

# 4.2 
brute_force_knapsack(x = knapsack_objects [1: 8,], W = 3500)
brute_force_knapsack(x = knapsack_objects [1:12,], W = 3500)
brute_force_knapsack(x = knapsack_objects [1: 8,], W = 2000)
brute_force_knapsack(x = knapsack_objects [1:12,], W = 2000)
```
Question How much time does it take to run the algorithm for n = 16 objects?

Answer: 0.72

# 4.3

```{r}
greedy_knapsack (x = knapsack_objects [1: 800,], W = 3500)
greedy_knapsack (x = knapsack_objects [1: 1200,], W = 2000)
```

Question How much time does it take to run the algorithm for n = 1000000 objects?

Answer: Elapsed 0.22
So the aproximation is alot faster.

# 4.4

Question What performance gain could you get by trying to improve your code?

Answer: Very lite, we could probably increase our gain if we used matrix algebra instead of for-loops. 
